---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis build status](https://travis-ci.org/ITSLeeds/OSMtools.svg?branch=master)](https://travis-ci.org/ITSLeeds/OSMtools) [![Coverage status](https://codecov.io/gh/ITSLeeds/OSMtools/branch/master/graph/badge.svg)](https://codecov.io/github/ITSLeeds/OSMtools?branch=master) [![Build status](https://ci.appveyor.com/api/projects/status/gqp3smc04as3qg85?svg=true)](https://ci.appveyor.com/project/layik/OSMtools-05ana) [![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)


# OSMtools

R wrappers for [OSM Filter](https://wiki.openstreetmap.org/wiki/Osmfilter) and [OSM Convert](https://wiki.openstreetmap.org/wiki/Osmconvert) and functions for downloading from [geofabrik](https://www.geofabrik.de/data/download.html). The package makes it easier to download and use large [Open Street Map](https://www.openstreetmap.org)  files with R.

**Note**: The package is currently windows only

## Installation

Install the package with **remotes** as follows:

```{r install, eval=FALSE}
install.packages("remotes") # If you do not already have the remotes package
remotes::install_github("ITSleeds/OSMTools")
```

## Usage

This R package provides a userfiendly interface to the Windows command line tools osmfilter.exe and osmconvert.exe. For example, if you wanted to get the road in your local area.

You can download a section of the OSM for your local area from Geofabrik.

```{r, eval=FALSE}
osmt_geofabrik_dl(region = "europe/great-britain/england/west-yorkshire", destfile = "wy.pbf")
```

Then convert the PBF file into a format that can be edited.

```{r, eval=FALSE}
osmt_convert(file = "wy.pbf", format_out = "o5m")
```

Then make a new file with just the roads.

```{r, eval=FALSE}
osmt_filter(file = "wy.o5m", path_out = "wy_roads.o5m", keep = "highway=")
```


## Contribution

Please note that the `OSMtools` project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.


## Package Status

This package is part of ongoing research at the University of Leeds, it is provided "as is" and is likely to be updated and changed without warning to meet the research needs of the University.
